---
title: "Untitled"
author: "The Spanish Inquisition"
date: "April 28, 2019"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##### Question 1 #####

##I chose KIF11. This protein is in control of spindle coding and cell division.

###Accession Number = P52732
###Species related with = Homo sapiens

##### Question 2 #####

## Genetic code set at "Standard (1)".
## Database search set defined as "Non-redundant protein sequences (nr)".
## Because of CPU limits, I've set the query limit from 1 to 1500.
### Despite this, strains with statistically significant e-values were produced.


##### Question 3 #####

# Gathering information about this protein:

## FASTA Sequence:
```{r}
# >NP_004514.2 kinesin-like protein KIF11 [Homo sapiens]
# MASQPNSSAKKKEEKGKNIQVVVRCRPFNLAERKASAHSIVECDPVRKEVSVRTGGLADKSSRKTYTFDM
# VFGASTKQIDVYRSVVCPILDEVIMGYNCTIFAYGQTGTGKTFTMEGERSPNEEYTWEEDPLAGIIPRTL
# HQIFEKLTDNGTEFSVKVSLLEIYNEELFDLLNPSSDVSERLQMFDDPRNKRGVIIKGLEEITVHNKDEV
# YQILEKGAAKRTTAATLMNAYSSRSHSVFSVTIHMKETTIDGEELVKIGKLNLVDLAGSENIGRSGAVDK
# RAREAGNINQSLLTLGRVITALVERTPHVPYRESKLTRILQDSLGGRTRTSIIATISPASLNLEETLSTL
# EYAHRAKNILNKPEVNQKLTKKALIKEYTEEIERLKRDLAAAREKNGVYISEENFRVMSGKLTVQEEQIV
# ELIEKIGAVEEELNRVTELFMDNKNELDQCKSDLQNKTQELETTQKHLQETKLQLVKEEYITSALESTEE
# KLHDAASKLLNTVEETTKDVSGLHSKLDRKKAVDQHNAEAQDIFGKNLNSLFNNMEELIKDGSSKQKAML
# EVHKTLFGNLLSSSVSALDTITTVALGSLTSIPENVSTHVSQIFNMILKEQSLAAESKTVLQELINVLKT
# DLLSSLEMILSPTVVSILKINSQLKHIFKTSLTVADKIEDQKKELDGFLSILCNNLHELQENTICSLVES
# QKQCGNLTEDLKTIKQTHSQELCKLMNLWTERFCALEEKCENIQKPLSSVQENIQQKSKDIVNKMTFHSQ
# KFCADSDGFSQELRNFNQEGTKLVEESVKHSDKLNGNLEKISQETEQRCESLNTRTVYFSEQWVSSLNER
# EQELHNLLEVVSQCCEASSSDITEKSDGRKAAHEKQHNIFLDQMTIDEDKLIAQNLELNETIKIGLTKLN
# CFLEQDLKLDIPTGTTPQRKSYLYPSTLVRTEPREHLLDQLKRKQPELLMMLNCSENNKEETIPDVDVEE
# AVLGQYTEEPLSQEPSVDAGVDCSSIGGVPFFQHKKSHGKDKENRGINTLERSKVEETTEHLVTKSRLPL
# RAQINL
```

### The novel protein is found on an organism called Piliocolobus tephrosceles, or Ugandan red colobus - a monkey.

### The protein's name is kinesin-like protein KIF11.


##### Question 4 #####

## Proving that this gene and its corresponding protein are novel.

### The proteins are indeed novel. Even though the blastp's first result, kinesin-like protein KIF11 [Cebus capucinus imitator], had a 100% percentage identical, it is from a different species. Thus satisfying the criteria of being a novel protein.



##### Question 5/6 #####

## Take a look at the picture here with this Imgur link.

#### https://imgur.com/a/QDkhqS7

#### JAO87825.1 - KIF11, Poeciliopsis prolifica
#### RLQ59498.1 - KIF11, Cricetulus griseus
#### RLQ57887.1 - KIF11, partial, Cricetulus griseus
#### OWK07780.1 - KIF11, Cervus elaphus hippelaphus
#### NP_004514.2 - KIF11, Homo sapiens

##### We see with this image, that at some point in time, the KIF11 from C.e. hippelaphus have split and became the KIF11 from C. griseus. The KIF11 from the humans and P. prolifica share a common ancestor with all other organisms, but no KIF11 has split from the humans or P. prolifica at any point in time.



##### Question 7 ######

```{r}

# Generating the heatmap.

kif11pdb <- c("3ZCW", "5JV3", "3K5E")
get.pdb(kif11pdb)

x <- read.fasta("FBKDCF5G211-alignment.fa") # Multiple alignment fasta file that aligns the 5 data labeled above in Questions 5 and 6.

heatmap.data <- seqidentity(x)

heatmap(heatmap.data)



```

##### Question 8 #####
```{r}
main.seq.anal <- blast.pdb("NP_004514.2")

View(main.seq.anal)

plot.blast(main.seq.anal,
           cutoff = 100,
           cex = 0.9)



```



# Note to future self: Get VMD on PC, then complete 9 and 10. Should be easy enough?
pull
