---
title: "Class 12"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Prep for docking

```{r}
library(bio3d)
file <- get.pdb("1hsg")
pdb <- read.pdb(file)
prot <- atom.select(pdb, "protein", value=TRUE)
write.pdb(prot, file="1hsg_protein.pdb")
```

```{r}
lig <- atom.select(pdb, "ligand", value = T)
write.pdb(lig, file = "1hsg_ligand.pdb")
```

##  Q2: Can you locate the binding site visually? Note that crystal structures normally lack hydrogen atoms, why?

### Yes. The binding site for this protein is represented with yellow bonds. Crystal structures normally lack hydrogen atoms because H atoms are small, and many are present in a structure. So when graphically represented, they can be a bit messy and hard to understand, and that's why H atoms are not represented by default.


# The .pdbqt file allows for a more in depth look into the atoms of the pdb. As in, the pdbqt files list the charges, atom types, etc. on the file itself.


## Q3: Look at the charges. Does it make sense (e.g. based on your knowledge of the physiochemical properties of amino acids)?

### Yes it makes sense. For instance, N (Asparagine) is listed as a negative charge. Asparagine is a polar AA, existing as either a proton donator or an acceptor. The negative charge denotes that Asparagine is a proton acceptor.

# Accessing the allpdbqt file.

```{r}
res <- read.pdb ("all.pdbqt", multi = T)

write.pdb(res, "results.pdb")
```

##  Q4: Qualitatively, how good are the docks? Is the crystal binding mode reproduced? Is it the best conformation according to AutoDock Vina?

### The VMD loops 14 times, and that's for each active "torsions" denoted in the all.pdbqt file. A high affinity ligand is not optimal - they are toxic, non-binding, and difficult to synthesize.


```{r}
res <- read.pdb("all.pdbqt", multi = T)
ori <- read.pdb("1hsg_ligand.pdbqt")
rmsd(ori, res)
```



## Normal mode analysis in Bio3D.

```{r}
pdb <- read.pdb("1hel")
modes <- nma(pdb)
plot(modes, sse = pdb)
mktrj(modes, mode = 7, file = "nma.pdb")


```


