---
title: 'Class 7: R function and packages'
author: "Sanghun Lee"
date: "April 23, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#### Functions revisited

We will source a file from online with our functions from last day

```{r}
source("http://tinyurl.com/rescale-R")
```

Try out the last day's rescale() function

```{r}
rescale(1:10)
```

Try the rescale function that catches string inputs
```{r}
rescale2(c(1:10), "string")
```


```{r}
x <- c(1, 2, NA, 3, NA)
y <- c(NA, 3, NA, 3, 4)
```

```{r}
#Always start with a simple definition of the problem!
#Use other default functions to see if our assessment is true!

#Start with a simple example of the larger problem I am trying to solve

is.na(x)

is.na(y)

```

Put these together with an AND
```{r}
is.na(x) | is.na(y)
```
Take the sum() to find out how many TRUE values we hae and thus how many NAs we had in both x and y

```{r}
sum(is.na(x) & is.na(y))
```

Now I can make this into a function!

```{r}
both_na <- function(x, y){
  sum(is.na(x) & is.na(y))
  
}
```

Test, test, test
```{r}
x <- c(NA, NA, NA)
y1 <- c(1< NA, NA)
y2 <- c(1, NA, NA, NA)
y3 <- c(1, NA, NA, NA, NA, NA, NA)
both_na(x, y3)
```


```{r}
which(is.na(c(1, 2, NA, 4)))
#prints the position of our NA in the vector. It's in 3!

```







#### Follow Along!

##### Intersect Function
```{r}

x <- df1$IDs
y <- df2$IDs

x
y

intersect(x, y)

which(x %in% y)
```

```{r}
x[x %in% y]
```


```{r}

gene_intersect <- function(x, y) {
  cbind( x[x %in% y],
         y[y %in% x])
}
#Code -> Extract Function -> Name function!
```

```{r}
gene_intersect2(df1, df2)
```

```{r}
gene_intersect3(df1, df2)
```

```{r}
gene_intersect4(df1, df3)
```


```{r}
Andy <- c(100, 100, 100, 100, 100, 100, 90)
Sarah <- c(100, 90, 90, 90, 90, 90, 97, 80)

grade <- function(x){
  min(x)
  x1 <- x[x!=min(x)]
  paste("The average grade is:", round(mean(x1), digits = 2))
}
```

